---
title: "A1"
author: "costanzadeacutis"
date: "2023-01-20"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
rm(list=ls())

# Import libraries
library(tidyverse)
library(lspline)
library(cowplot)
library(ggplot2)
library(boot)
library(estimatr)
library(huxtable)
library(stargazer)
library(modelsummary)
library(janitor)
library(fixest)
library(grid)
library(caret)

knitr::opts_chunk$set(echo = TRUE)
```

# Dataset

I import the csv data

```{r dataset}
cps <- read_csv("morg-2014-emp.csv", 
                     col_types = cols(.default = "?"))
```

# Select occupation 

I retain 2 occupation types 
- Artists and related workers
- Food Preparation and Serving Related Occupations

```{r occupations}
cps <- cps %>% mutate(sample=ifelse(occ2012==2600,1,
                                              ifelse(cps$occ2012>=4000 & cps$occ2012<=4150,2,0)))

cps <- cps %>% filter(sample==1 | sample==2)

glimpse(cps)
```

# Create variables 

I generate the target variable and re-specify some predictors 

```{r variables}

# Earnings per hour (level and log), female, and age squared
cps <- cps %>% mutate(earnhours=earnwke/uhours, 
                      lnw=log(earnhours+1), # to avoid negative values
                      female=as.numeric(sex==2),
                      agesq=age^2
)

# Race 
cps <- cps %>% mutate(white=as.numeric(race==1),
                      afram = as.numeric(race==2),
                      asian = as.numeric(race==4),
                      hisp = ifelse(!is.na(ethnic),1,0),
                      othernonw = as.numeric(white==0 & afram==0 & asian==0 & hisp==0),
                      nonUSborn = as.numeric(prcitshp=="Foreign Born, US Cit By Naturalization" | prcitshp=="Foreign Born, Not a US Citizen") 
)

# Education
cps <- cps %>% mutate(ed_lessBA=as.numeric(grade92<43),
                      ed_BA=as.numeric(grade92==43),
                      ed_MA=as.numeric(grade92==44),
                      ed_Profess = as.numeric(grade92==45),
                      ed_PhD = as.numeric(grade92==46)
)

# Marital status and children
cps <- cps %>% mutate(married = as.numeric(marital==1 | marital==2),
                      divorced = as.numeric(marital==3 | marital==5 | marital==6),
                      wirowed = as.numeric(marital==4),
                      nevermar = as.numeric(marital==7),
                      
                      child0 = as.numeric(chldpres==0),
                      child1 = as.numeric(chldpres==1),
                      child2 = as.numeric(chldpres==2),
                      child3 = as.numeric(chldpres==3),
                      child4pl = as.numeric(chldpres>=4)
)

# Work-related variables
cps <- cps %>% mutate(fedgov = as.numeric(class=="Government - Federal"),
                      stagov = as.numeric(class=="Government - State"),
                      locgov = as.numeric(class=="Government - Local"),
                      nonprof = as.numeric(class=="Private, Nonprofit"),
                      ind2dig = as.integer(as.numeric(as.factor(ind02))/100),
                      occ2dig = as.integer(occ2012/100),
                      union = as.numeric(unionmme=="Yes" | unioncov=="Yes")
)

```

# Data summary

I look at some summary statistics for earnings per hour and predictors. I retain only values of earnings per hour equal or above 1$.

```{r datasummary}

cps %>% dplyr::select(earnwke,uhours,earnhours) %>% summary()

cps %>% filter(earnhours>=1) %>% dplyr::select(earnwke,uhours,earnhours) %>% summary()

cps <- cps %>% filter(earnhours>=1)

datasummary(earnhours + lnw + female + age + white + afram + asian + hisp + othernonw + nonUSborn + ed_lessBA + ed_BA + ed_MA + ed_Profess + ed_PhD + married + divorced + wirowed + nevermar + child0 + child1 + child2 + child3 + child4pl + fedgov + stagov + locgov + nonprof + ind2dig + occ2dig + union ~
               Mean + Median + Min + Max + P25 + P75 + N, data = cps)

```

# Graphical anaylsis of earnings per hour

```{r graphs}

# for the entire sample 
ggplot(data=cps, aes(x=earnhours)) +
  geom_histogram(aes(y = (after_stat(count))/sum(after_stat(count))), binwidth = 1, boundary=0,
                 fill = 'navyblue', color = 'white', size = 0.25, alpha = 0.8,  show.legend=F, na.rm=TRUE) +
  coord_cartesian(xlim = c(0, 280)) +
  labs(x = 'Earnings per hour',y = 'Percent')+
  theme_bw() +
  expand_limits(x = 0.01, y = 0.01) +
  scale_y_continuous(expand = c(0.01,0.01),labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(expand = c(0.01,0.01),breaks = seq(0,280, 40))

# Should the extreme values be excluded?

# looking closer to those earnings per hour below 70
ggplot(data=cps, aes(x=earnhours)) +
  geom_histogram(aes(y = (..count..)/sum(..count..)), binwidth = 1, boundary=0,
                 fill = 'navyblue', color = 'white', size = 0.25, alpha = 0.8,  show.legend=F, na.rm=TRUE) +
  coord_cartesian(xlim = c(0, 70)) +
  labs(x = 'Earnings per hour',y = 'Percent')+
  theme_bw() +
  expand_limits(x = 0.01, y = 0.01) +
  scale_y_continuous(expand = c(0.01,0.01),labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(expand = c(0.01,0.01),breaks = seq(0,70, 5))


```

# Models and estimations

Target: earnings per hour

First level regressions
Predictors:
1. female, age, age^2
2. female, age, age^2, race
3. female, age, age^2, race, work, educ
4. female, age, age^2, race x age, work x age, educ x age

```{r models}

model1 <- as.formula(earnhours ~ female + age + agesq)
model2 <- as.formula(earnhours ~ female + age + agesq + afram + asian + hisp + othernonw + nonUSborn)
model3 <- as.formula(earnhours ~ female + age + agesq + afram + asian + hisp + othernonw + nonUSborn + ind2dig + occ2dig + union + ed_BA + ed_MA + ed_Profess + ed_PhD)
model4 <- as.formula(earnhours ~ female + age + agesq + afram*age + asian*age + hisp*age + othernonw*age + nonUSborn*age + ind2dig*age + occ2dig*age + union*age + ed_BA*age + ed_MA*age + ed_Profess*age + ed_PhD*age)

# OLS
reg1 <- feols(model1, data=cps, vcov = 'hetero')
reg2 <- feols(model2, data=cps, vcov = 'hetero')
reg3 <- feols(model3, data=cps, vcov = 'hetero')
reg4 <- feols(model4, data=cps, vcov = 'hetero')

```

# Evaluate models

Look at BIC and RMSE in the full sample

```{r evaluating}

fitstat_register('k', function(x){length(x$coefficients) - 1}, 'No. Variables')
etable(reg1, reg2, reg3, reg4, fitstat = c('bic','rmse','r2','n','k'))

```



