---
title: "A2-datacleaning"
author: "costanzadeacutis"
date: "2023-01-24"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
rm(list=ls())

# Import libraries
library(tidyverse)
library(lspline)
library(cowplot)
library(ggplot2)
library(boot)
library(estimatr)
library(huxtable)
library(stargazer)
library(modelsummary)
library(janitor)
library(fixest)
library(grid)
library(caret)

knitr::opts_chunk$set(echo = TRUE)
```

# Upload data: listings of Milano

I drop the variables that I am not planning to use because they are
1. websites/url
2. ids not identifying the specific house/apartment
3. empty (ex. neighbourhood_group_cleansed)
4. not useful for the aim of the analysis

I then save the resulting dataset and I perform some basic cleaning on id variable

```{r cleaning}

data <- read.csv("listings.csv")

#drop not useful variables
drops <- c("listing_url", "scrape_id", "last_scraped", "source", "picture_url", "host_url", "host_thumbnail_url", "host_picture_url", "description", "neighborhood_overview", "host_about", "host_neighbourhood", "calendar_updated", "neighbourhood_group_cleansed", "license", "minimum_minimum_nights", "minimum_maximum_nights", "maximum_minimum_nights", "maximum_maximum_nights", "minimum_nights_avg_ntm", "maximum_nights_avg_ntm", "availability_30", "availability_60", "availability_90", "availability_365", "latitude", "longitude")

data <- data[ , !(names(data) %in% drops)]

#save the resulting dataset
write.csv(data,file="airbnb_milano_listing.csv")

df <- read.csv("airbnb_milano_listing.csv",
             sep=",",header = TRUE, stringsAsFactors = FALSE)

#drop broken lines - where id is not a character of numbers
df$junk <- grepl("[[:alpha:]]", df$id)
df <- subset(df, df$junk==FALSE)
df <- df[1:ncol(df)-1]              

```

## Formatting columns

I remove the symbols: % and $
I transform 2 varables from categorical to numerical and I format binary variables 

```{r formatting}
#remove percentage signs
for (perc in c("host_response_rate","host_acceptance_rate")){
  df[[perc]]<-gsub("%","",as.character(df[[perc]]))
}

#remove dollar signs
for (pricevars in c("price")){
  df[[pricevars]]<-gsub("\\$","",as.character(df[[pricevars]]))
  df[[pricevars]]<-gsub("\\,","",as.character(df[[pricevars]]))
  df[[pricevars]]<-as.numeric(as.character(df[[pricevars]]) )
}

#numerical
df <- df %>%
  mutate(p_host_acceptance_rate = as.numeric(host_acceptance_rate),
    p_host_response_rate = as.numeric(host_response_rate))
  
#format binary variables
for (binary in c("host_is_superhost","host_has_profile_pic","host_identity_verified", "has_availability", "instant_bookable")){
  df[[binary]][df[[binary]]=="f"] <- 0
  df[[binary]][df[[binary]]=="t"] <- 1
}
```

## Creation of variables
### Amenities
For Milano, there are too many different amenities that can be reclassified in simpler groups (ex. all the shampoo brands and other bathroom products/characteristics can be put together)

```{r amenities, warning=FALSE}
#amenities
df$amenities<-gsub("\\[","",df$amenities)
df$amenities<-gsub("\\]","",df$amenities)
df$amenities<-gsub('\\"',"",df$amenities)
df$amenities<-tolower(df$amenities)
df$amenities<-as.list(strsplit(df$amenities, ","))

#define levels and dummies 
levs <- levels(factor(unlist(df$amenities)))

#group similar amenities
bathroom_essentials <- "shampoo|soap|conditioner|acqua di parma|balea|dove|elseve|felce azzurra|garnier|hermes|shower gel|saponi|infasil|kerastase|oreal|marsiglia|neutro roberts|nivea|panten|palmolive|perlier|spuma di|sunsil|yves rocher|clear|bathroom essential|hot water"
fridge <- "refrigerator|freezer|fridge"
tv <- "standard cable|standard tv|premium cable|dvd player|hdtv|[123456][0123456789]\\\\ tv"
smart_tv <- "netflix|prime video|primevideo|amazon prime|apple tv|chromecast|disney+|roku|fire tv|hbo max|hulu|infinity"
sound_system <- "casse|sound system|bose|record player"
ac <- "ac|air conditioning|ceiling fan|portable fans"
wardrobe <- "closet|dresser|wardrobe|hangers|clothing storage"
baby_kit <- "baby bath|baby monitor|baby safety|booster seat|high chair|crib|outlet covers|table corner guards|babysitter recommendations"
kitchen_amenities <- "cooking basics|kitchen|hot water kettle|microwave|baking|blender|bread maker|toaster|rice maker|whirlpool mwp|wine glasses|dishes and silverware|coffee|espresso machine|french press|nespresso|hotpoint ariston"
bedroom_essentials <- "bed linens|bedroom comforts|extra pillows"
reading_material <- "books|reading"
exercise_equip <- "exercise equipment|weights|stationary bike|treadmill|yoga mat"
reserved_parking <- "carport|free parking|garage|paid parking|driveway parking|paid valet parking"
heating <- "heated|heating|heater"
outdoor_furniture <- "sun loungers|outdoor furniture|pool cover|hammock|bbq|barbecue|outdoor dining area|outdoor shower"

tables <- "changing table|dining table"
special_view <- "canal view|city skyline view|courtyard view|garden view|golf course view|harbor view|lake view|marina view|mountain view|park view|pool view|resort view|river view|waterfront"
security <- "carbon monoxide alarm|first aid kit|fire extinguisher|lock on bedroom door|safe|security cameras|window guards|smoke alarm"
gym <- "gym"
games <- "game console|board games|ping pong table|pool toys|pool table"
pool <- "olympic-sized|pool"
hot_tub <- "hot tub"
sauna <- "sauna"
fire_pit <- "fire pit|wood-burning"
keypad <- "keypad|smart lock|lockbox|self check-in"
windows_amenities <- "mosquito net|room-darkening shades"

#modify levs based on groups of amenities
levs[str_detect(levs, paste(bathroom_essentials, collapse = "|"))] <- "bathroom essentials"
levs[str_detect(levs, paste(fridge, collapse = "|"))] <- "fridge"
levs[str_detect(levs, "oven")] <- "oven"
levs[str_detect(levs, "stove")] <- "stove"
levs[str_detect(levs,  paste(tv, collapse = "|"))] <- "tv"
levs[str_detect(levs, paste(smart_tv, collapse = "|"))] <- "smart tv"
levs[str_detect(levs, "wifi")] <- "wifi"
levs[str_detect(levs, paste(sound_system, collapse = "|"))] <- "sound system"
levs[str_detect(levs, paste(ac, collapse = "|"))] <- "ac"
levs[str_detect(levs, paste(wardrobe, collapse = "|"))] <- "wardrobe"
levs[str_detect(levs, paste(baby_kit, collapse = "|"))] <- "baby kit"
levs[str_detect(levs, "children")] <- "toys for children"
levs[str_detect(levs, paste(kitchen_amenities, collapse = "|"))] <- "kitchen amenities"
levs[str_detect(levs, paste(bedroom_essentials, collapse = "|"))] <- "bedroom essentials"
levs[str_detect(levs, paste(reading_material, collapse = "|"))] <- "reading material"
levs[str_detect(levs, "washer")] <- "washing machine"
levs[str_detect(levs, "dryer")] <- "dryer"
levs[str_detect(levs, paste(exercise_equip, collapse = "|"))] <- "exercise equip"
levs[str_detect(levs, paste(reserved_parking, collapse = "|"))] <- "reserved parking"
levs[str_detect(levs, "street parking")] <- "unreserved parking"
levs[str_detect(levs, paste(games, collapse = "|"))] <- "games"
levs[str_detect(levs, paste(heating, collapse = "|"))] <- "heating"
levs[str_detect(levs, "laundromat")] <- "external laudry"
levs[str_detect(levs, "perfect for the essential")] <- "essentials"
levs[str_detect(levs, paste(outdoor_furniture, collapse = "|"))] <- "outdoor furniture"
levs[str_detect(levs, paste(special_view, collapse = "|"))] <- "special view"
levs[str_detect(levs, paste(security, collapse = "|"))] <- "security"
levs[str_detect(levs, paste(gym, collapse = "|"))] <- "gym"
levs[str_detect(levs, paste(sauna, collapse = "|"))] <- "sauna"
levs[str_detect(levs, paste(hot_tub, collapse = "|"))] <- "hot tub"
levs[str_detect(levs, paste(pool, collapse = "|"))] <- "pool"
levs[str_detect(levs, paste(tables, collapse = "|"))] <- "table"
levs[str_detect(levs, "patio or balcony")] <- "patio or balcony"
levs[str_detect(levs, paste(fire_pit, collapse = "|"))] <- "fire pit"
levs[str_detect(levs, paste(keypad, collapse = "|"))] <- "keypad"
levs[str_detect(levs, paste(windows_amenities, collapse = "|"))] <- "windows amenities"
levs <- trimws(levs)
levs <- unique(levs)

#remove certain patterns that do not express any amenity
to_delete2 <- "depending on availability|clear|years old|diversi marchi|host greets you|open 24 hours|open specific hours|ski-in|long term stays allowed|single level home"

levs[str_detect(levs, paste(to_delete2, collapse = "|"))] <- NA
levs[1] <- NA

levs <- na.omit(levs)

#create dummies in dataset
df <- cbind(df,as.data.frame(do.call(rbind, lapply(lapply(df$amenities, factor, levs), table))))

#dummies that are groups of amenities have to be modified by hand

df$`bathroom essentials` <- ifelse(str_detect(df$amenities, paste(bathroom_essentials, collapse="|")),1,0)

df$`fridge` <- ifelse(str_detect(df$amenities, paste(fridge, collapse="|")),1,0)

df$`oven` <- ifelse(str_detect(df$amenities, "oven"),1,0)

df$`stove` <- ifelse(str_detect(df$amenities, "stove"),1,0)

df$`tv` <- ifelse(str_detect(df$amenities, paste(tv, collapse="|")),1,0)

df$`smart tv` <- ifelse(str_detect(df$amenities, paste(smart_tv, collapse="|")),1,0)

df$`wifi` <- ifelse(str_detect(df$amenities, "wifi"),1,0)

df$`sound system` <- ifelse(str_detect(df$amenities, paste(sound_system, collapse="|")),1,0)

df$`ac` <- ifelse(str_detect(df$amenities, paste(ac, collapse="|")),1,0)

df$`wardrobe` <- ifelse(str_detect(df$amenities, paste(wardrobe, collapse="|")),1,0)

df$`baby kit` <- ifelse(str_detect(df$amenities, paste(baby_kit, collapse="|")),1,0)

df$`toys for children` <- ifelse(str_detect(df$amenities, "children"),1,0)

df$`kitchen amenities` <- ifelse(str_detect(df$amenities, paste(kitchen_amenities, collapse="|")),1,0)

df$`bedroom essentials` <- ifelse(str_detect(df$amenities, paste(bedroom_essentials, collapse="|")),1,0)

df$`reading material` <- ifelse(str_detect(df$amenities, paste(reading_material, collapse="|")),1,0)

df$`washing machine` <- ifelse(str_detect(df$amenities, "washer"),1,0)

df$`dryer` <- ifelse(str_detect(df$amenities, "dryer"),1,0)

df$`exercise equipm` <- ifelse(str_detect(df$amenities, paste(exercise_equip, collapse="|")),1,0)

df$`reserved parking` <- ifelse(str_detect(df$amenities, paste(reserved_parking, collapse="|")),1,0)

df$`unreserved parking` <- ifelse(str_detect(df$amenities, "street parking"),1,0)

df$`games` <- ifelse(str_detect(df$amenities, paste(games, collapse="|")),1,0)

df$`heating` <- ifelse(str_detect(df$amenities, paste(heating, collapse="|")),1,0)

df$`external laundry` <- ifelse(str_detect(df$amenities, "laundromat"),1,0)

df$`essentials` <- ifelse(str_detect(df$amenities, "perfect for the essential"),1,0)

df$`outdoor furniture` <- ifelse(str_detect(df$amenities, paste(outdoor_furniture, collapse="|")),1,0)

df$`special view` <- ifelse(str_detect(df$amenities, paste(special_view, collapse="|")),1,0)

df$`security` <- ifelse(str_detect(df$amenities, paste(security, collapse="|")),1,0)

df$`gym` <- ifelse(str_detect(df$amenities, paste(gym, collapse="|")),1,0)

df$`hot tub` <- ifelse(str_detect(df$amenities, paste(hot_tub, collapse="|")),1,0)

df$`sauna` <- ifelse(str_detect(df$amenities, paste(sauna, collapse="|")),1,0)

df$`pool` <- ifelse(str_detect(df$amenities, paste(pool, collapse="|")),1,0)

df$`table` <- ifelse(str_detect(df$amenities, paste(tables, collapse="|")),1,0)

df$`patio or balcony` <- ifelse(str_detect(df$amenities, "patio or balcony"),1,0)

df$`fire pit` <- ifelse(str_detect(df$amenities, paste(fire_pit, collapse="|")),1,0)

df$`keypad` <- ifelse(str_detect(df$amenities, paste(keypad, collapse="|")),1,0)

df$`windows amenities` <- ifelse(str_detect(df$amenities, paste(windows_amenities, collapse="|")),1,0)

df$`bathtub` <- ifelse(str_detect(df$amenities, "bathtub"),1,0)
df$`bidet` <- ifelse(str_detect(df$amenities, "bidet"),1,0)
df$`bikes` <- ifelse(str_detect(df$amenities, "bikes"),1,0)
df$`breakfast` <- ifelse(str_detect(df$amenities, "breakfast"),1,0)
df$`building staff` <- ifelse(str_detect(df$amenities, "building staff"),1,0)
df$`cleaning available during stay` <- ifelse(str_detect(df$amenities, "cleaning available during stay"),1,0)
df$`cleaning products` <- ifelse(str_detect(df$amenities, "cleaning products"),1,0)
df$`elevator` <- ifelse(str_detect(df$amenities, "elevator"),1,0)
df$`ethernet connection` <- ifelse(str_detect(df$amenities, "ethernet connection"),1,0)
df$`ev charger` <- ifelse(str_detect(df$amenities, "ev charger"),1,0)
df$`iron` <- ifelse(str_detect(df$amenities, "iron"),1,0)
df$`luggage dropoff allowed` <- ifelse(str_detect(df$amenities, "luggage dropoff allowed"),1,0)
df$`pets allowed` <- ifelse(str_detect(df$amenities, "pets allowed"),1,0)
df$`piano` <- ifelse(str_detect(df$amenities, "piano"),1,0)
df$`private entrance` <- ifelse(str_detect(df$amenities, "private entrance"),1,0)
df$`private living room` <- ifelse(str_detect(df$amenities, "private living room"),1,0)
df$`rooftop` <- ifelse(str_detect(df$amenities, "rooftop"),1,0)
df$`smooking allowed` <- ifelse(str_detect(df$amenities, "smoking allowed"),1,0)
df$`suitable for events` <- ifelse(str_detect(df$amenities, "suitable for events"),1,0)
```

### Days since first review
This variable expresses the number of days from the time of the first review to that of the last scraping

```{r days since first review}
#create days since first review
df <- df %>%
  mutate(
    n_days_since = as.numeric(as.Date(calendar_last_scraped,format="%Y-%m-%d") -
                                as.Date(first_review ,format="%Y-%m-%d")))
```



### Host verification
As for amenities, I create dummies related to the type of host verification available

```{r host verification}
#host verif
df$host_verifications<-gsub("\\[","",df$host_verifications)
df$host_verifications<-gsub("\\]","",df$host_verifications)
df$host_verifications<-gsub("\\'","",df$host_verifications)
df$host_verifications<-gsub(" ","",df$host_verifications)
df$host_verifications<-as.list(strsplit(df$host_verifications, ","))

#define levels and dummies 
levs2 <- levels(factor(unlist(df$host_verifications)))
df<-cbind(df,as.data.frame(do.call(rbind, lapply(lapply(df$host_verifications, factor, levs2), table))))

df <- df %>% 
  rename(host_verif_phone = phone,
         host_verif_email = email,
         host_verif_wemail = work_email
         )
```


### Bathrooms
The variable bathrooms is categorical. I separate the numerical part (expressed by numbers or by "half...") from the description "shared" or "private". For the latter, I create a separate variable "bathrooms_type", which I factorize.

```{r bathrooms}
#number of bathrooms
df$bathrooms <- as.numeric(gsub("([0-9]+).*$", "\\1", df$bathrooms_text))
df$bathrooms[str_detect(df$bathrooms_text, "Half-bath|Shared half-bath")] <- 0.5
#types of bathrooms
df$bathrooms_type[str_detect(df$bathrooms_text, "[Ss]hared")] <- "Shared"
df$bathrooms_type[str_detect(df$bathrooms_text, "[Pp]rivate")] <- "Private"

df <- df %>%
  mutate(f_bathrooms_type = factor(bathrooms_type))
```

### Municipi
Given that the neighboorhoods are too many and too small, I regrouped them in "municipi": this categorization comes from comune.milano.it. I then factorize them.

Note: municipio_2_9 is area between Municipio 2 and Municipio 9, that could not be categorized in any of the two.

```{r municipi}
#first analyze which neighboorhoods are present
unique(df$neighbourhood_cleansed)
#clean 
df$neighbourhood_cleansed[str_detect(df$neighbourhood_cleansed, "\u0085")] <- "PARCO BOSCO IN CITTA'"

#categorize them into Municipi
Municipio1 <- c("DUOMO", "MAGENTA - S. VITTORE", "GUASTALLA", "TICINESE", "BRERA", "PARCO SEMPIONE")
Municipio2 <- c("VIALE MONZA", "CENTRALE", "PADOVA", "LORETO", "ADRIANO", "GRECO")
Municipio3 <- c("BUENOS AIRES - VENEZIA", "CITTA' STUDI", "PARCO LAMBRO - CIMIANO", "LAMBRATE", "GIARDINI PORTA VENEZIA")
Municipio4 <- c("XXII MARZO", "UMBRIA - MOLISE", "LODI - CORVETTO", "PORTA ROMANA", "ORTOMERCATO", "CORSICA", "MECENATE", "TRIULZO SUPERIORE", "ROGOREDO", "PARCO MONLUE' - PONTE LAMBRO")
Municipio5 <- c("TIBALDI", "VIGENTINA", "GRATOSOGLIO - TICINELLO", "STADERA", "SCALO ROMANA", "RIPAMONTI", "EX OM - MORIVIONE", "CHIARAVALLE", "PARCO DELLE ABBAZIE", "CANTALUPA", "QUINTOSOLE")
Municipio6 <- c("NAVIGLI", "WASHINGTON", "TORTONA", "BANDE NERE", "GIAMBELLINO", "S. CRISTOFORO", "RONCHETTO SUL NAVIGLIO", "BARONA", "LORENTEGGIO", "PARCO DEI NAVIGLI")
Municipio7 <- c("DE ANGELI - MONTE ROSA", "FORZE ARMATE", "BAGGIO", "PAGANO", "S. SIRO", "SELINUNTE", "PARCO BOSCO IN CITTA'", "FIGINO", "QUARTO CAGNINO", "QUINTO ROMANO", "MUGGIANO", "RONCHETTO DELLE RANE")
Municipio8 <- c("VILLAPIZZONE", "PARCO FORLANINI - ORTICA", "SARPI", "GALLARATESE", "GHISOLFA", "PORTELLO", "QT 8", "QUARTO OGGIARO", "MAGGIORE - MUSOCCO", "TRE TORRI", "TRENNO", "SACCO")
Municipio9 <- c("BICOCCA", "GARIBALDI REPUBBLICA", "ISOLA", "BOVISA", "BOVISASCA", "NIGUARDA - CA' GRANDA", "AFFORI", "DERGANO", "FARINI", "BRUZZANO", "PARCO NORD", "COMASINA")
Municipio_2_9 <- c("MACIACHINI - MAGGIOLINA")
Municipio_outside <- c("PARCO AGRICOLO SUD")

#create the municipio variable
df$municipio <- ifelse(df$neighbourhood_cleansed %in% Municipio1, "Municipio1",
                            ifelse(df$neighbourhood_cleansed %in% Municipio2, "Municipio2",
                                   ifelse(df$neighbourhood_cleansed %in% Municipio3, "Municipio3",
                                          ifelse(df$neighbourhood_cleansed %in% Municipio4, "Municipio4",
                                                 ifelse(df$neighbourhood_cleansed %in% Municipio5, "Municipio5",
                                                     ifelse(df$neighbourhood_cleansed %in% Municipio6, "Municipio6",
                                                            ifelse(df$neighbourhood_cleansed %in% Municipio7, "Municipio7",
                                                               ifelse(df$neighbourhood_cleansed %in% Municipio8, "Municipio8",
                                                                      ifelse(df$neighbourhood_cleansed %in% Municipio9, "Municipio9",
                                                                             ifelse(df$neighbourhood_cleansed %in% Municipio_2_9, "Municipio2-9", 
                                                                             ifelse(df$neighbourhood_cleansed %in% Municipio_outside, "Outside",
                                                        ".")))))))))))
#factor
df <- df %>%
  mutate(f_municipio = factor(municipio))

```


#### Drop variables modified
I drop those variables that I modified and I do not need anymore
```{r drop}
drops <- c("amenities", "host_verifications", "bathrooms_text", "host_response_rate", "host_acceptance_rate", "municipio", "bathrooms_type")
df <- df[ , !(names(df) %in% drops)]
```

#### rename some variables
For simplicity, I renamed some variables and I keep only those that I need

```{r rename}
# add new numeric columns from certain columns
numericals <- c("accommodates","bathrooms","number_of_reviews",
                "reviews_per_month","minimum_nights","beds","bedrooms")
df <- df %>%
  mutate_at(vars(numericals), funs("n"=as.numeric))

# rename columns so they start with n_ as opposed to end with _n
nnames <- df %>%
  select(ends_with("_n")) %>%
  names()

nnames_i <- match(nnames, colnames(df))

colnames(df)[nnames_i] <- paste0("n_", numericals)


# create dummy vars with amenities
dummies <- names(df)[seq(47,103)]

df <- df %>%
  mutate_at(vars(dummies), funs("d"= (.)))
# rename columns
dnames <- df %>%
  select(ends_with("_d")) %>%
  names()
dnames_i <- match(dnames, colnames(df))
colnames(df)[dnames_i] <- paste0("d_", tolower(gsub("[^[:alnum:]_]", "",dummies)))

colnames(df)

df2 <- df %>%
  select(name, id, price,
         neighbourhood_cleansed, room_type, property_type, review_scores_rating, matches("^n_.*|^f_.*|^p_.*|^d_.*"))

```


# Save and write 
I save a new csv file with data cleaned

```{r data cleaned}
#write csv
write.csv(df2,file="airbnb_milano_cleaned.csv")
```

