---
title: "A3prova"
author: "costanzadeacutis"
date: "2023-02-24"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
rm(list=ls())

# Import libraries
library(haven)
library(glmnet)
library(purrr)
library(margins)
library(skimr)
library(kableExtra)
library(Hmisc)
library(cowplot)
library(gmodels) 
library(lspline)
library(sandwich)
library(modelsummary)

library(rattle)
library(caret)
library(pROC)
library(ranger)
library(rpart)
library(partykit)
library(rpart.plot)

# load theme and functions
source("~/subdirectory/Assignment3/A3/A3/theme_bg.R") 
source("~/subdirectory/Assignment3/A3/A3/functions.R")

data_in <- "~/subdirectory/Assignment3/A3/A3"
data_out <- "~/subdirectory/Assignment3/A3/A3"
output <- "~/subdirectory/Assignment3/A3/A3/output/"
create_output_if_doesnt_exist(output)

knitr::opts_chunk$set(echo = TRUE)
```

# DATA PREPARATION

## Import data
I import dataset cs_bisnode_panel.csv which provides information on Scandinavian owned companies. I drop those variables with too many missing values and I retain only firm-year observations between 2010 and 2015.

```{r import, warning=FALSE}
data <- read_csv(paste(data_in,"cs_bisnode_panel.csv", sep = "/"))

# drop variables with many NAs
data <- data %>%
  select(-c(COGS, finished_prod, net_dom_sales, net_exp_sales, wages)) %>%
  filter(year !=2016)

#panel to use
data <- data %>%
  filter(year >= 2010,
         year <= 2015)
```

## Label engineering
I add the missing year and company id combinations; I also identify the companies that are "alive", i.e. sales greater than 0 and no missing value for sales 

```{r}
# add all missing year and comp_id combinations -
# originally missing combinations will have NAs in all other columns
data <- data %>%
  complete(year, comp_id)

# generate status_alive; if sales larger than zero and not-NA, then firm is alive
data  <- data %>%
  mutate(status_alive = sales > 0 & !is.na(sales) %>%
           as.numeric(.))

```

## Constructing the Target
### Employment
Ideally, to identify fast-growing firms, I would use employment: firms (with at least 5 or 10 employees, i.e. not too small) would be identified as fast-growing if their employment annualized growing rate were greater than a certain threshold (e.g. 20%). However, the variable for employment, labor_avg, expresses the monthly average employment in one year. I could look at other possible measures of growth, for example sales, but I believe fast growth of employment can better define fast-growing firms: sales could grow for one or two years just due to contingencies and non-structural growth; while, when a firm hires more employees, the expansions entails a more structural/intrinsic growth. 
Moreover, the variables labor_avg is noisy (there are 121990 NA values out of 236250 total observations, and 316 0 values) but also sales is almost as noisy (72386 NA and 28864 zeros), and the lost in observations is almost the same. Therefore, I choose to proceed with employment.

First, I remove the missing values from labor_avg and I drop observations where labor_avg==0.
Then, I look at the distribution (log does not change)

```{r}

Hmisc::describe(data$labor_avg)
#table(data$labor_avg)
Hmisc::describe(data$sales)
#table(data$sales)

# drop missing
data <- data %>%
  filter(!is.na(labor_avg))

# drop those that are 0
data <- data %>%
  filter(labor_avg>0.0069)


labor_avg_graph <- ggplot(data, aes(x=labor_avg)) +
  geom_histogram(binwidth = 0.1, fill = color[1], color = color.outline, alpha = 0.8, size = 0.1) +
  ylab("count") +
  xlab("labor_avg") +
  scale_x_continuous(expand = c(0.00,0.00),limits=c(0,5), breaks = seq(0,5, 0.5)) +
  theme_bg()
labor_avg_graph

#ln
data <- data %>%
  mutate(ln_labor_avg = log(labor_avg+1))

Hmisc::describe(data$ln_labor_avg)

ln_labor_avg_graph <- ggplot(data, aes(x=ln_labor_avg)) +
  geom_histogram(binwidth = 0.1, fill = color[1], color = color.outline, alpha = 0.8, size = 0.1) +
  ylab("count") +
  xlab("ln_labor_avg") +
  scale_x_continuous(expand = c(0.00,0.00),limits=c(0,3), breaks = seq(0,3, 0.5)) +
  theme_bg()
ln_labor_avg_graph

```

#### Target variable
I construct the annual growth rate variable for the labor_avg. I look at quantiles and I consider as fast growing those firms with growth above the 90th percentile (fast_growth is the target variable and it is per year).

```{r}
#define target

# generate annual employment growth rate
data <- data %>% 
  group_by(comp_id) %>%
  mutate(growth_labor = c(NA,diff(labor_avg))/lag(labor_avg, 1))

Hmisc::describe(data$growth_labor)

#target
data <- data %>%
  group_by(comp_id) %>%
  mutate(fast_growth = ifelse(growth_labor > 0.42105, 1, 0))
#above the 90th percentile
Hmisc::describe(data$fast_growth)

```

## Sales
First, I remove negative sales, create the logarithm of sales, re-scaled dividing by 1m, and growth rate. 
Then, I replace with 0 sales of new firms.

```{r}
summary(data$sales) # There will be NAs, we'll drop them soon

data <- data %>%
  mutate(sales = ifelse(sales < 0, 1, sales),
         ln_sales = ifelse(sales > 0, log(sales), 0),
         sales_mil=sales/1000000,
         sales_mil_log = ifelse(sales > 0, log(sales_mil), 0))
#growth rate of sales
data <- data %>%
  group_by(comp_id) %>%
  mutate(d1_sales_mil_log = sales_mil_log - Lag(sales_mil_log, 1) ) %>%
  ungroup()


# replace w 0 for new firms + add dummy to capture it
data <- data %>%
  mutate(age = (year - founded_year) %>%
           ifelse(. < 0, 0, .),
         new = as.numeric(age <= 1) %>% #  (age could be 0,1 )
           ifelse(balsheet_notfullyear == 1, 1, .),
         d1_sales_mil_log = ifelse(new == 1, 0, d1_sales_mil_log),
         new = ifelse(is.na(d1_sales_mil_log), 1, new),
         d1_sales_mil_log = ifelse(is.na(d1_sales_mil_log), 0, d1_sales_mil_log))
```

