---
title: "A3prova"
author: "costanzadeacutis"
date: "2023-02-24"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
rm(list=ls())

# Import libraries
library(haven)
library(glmnet)
library(purrr)
library(margins)
library(skimr)
library(kableExtra)
library(Hmisc)
library(cowplot)
library(gmodels) 
library(lspline)
library(sandwich)
library(modelsummary)

library(rattle)
library(caret)
library(pROC)
library(ranger)
library(rpart)
library(partykit)
library(rpart.plot)

# load theme and functions
source("~/subdirectory/Assignment3/A3/A3/theme_bg.R") 
source("~/subdirectory/Assignment3/A3/A3/functions.R")

data_in <- "~/subdirectory/Assignment3/A3/A3"
data_out <- "~/subdirectory/Assignment3/A3/A3"
output <- "~/subdirectory/Assignment3/A3/A3/output/"
create_output_if_doesnt_exist(output)

knitr::opts_chunk$set(echo = TRUE)
```

# DATA PREPARATION

## Import data
I import dataset cs_bisnode_panel.csv which provides information on Scandinavian owned companies. I drop those variables with too many missing values and I retain only firm-year observations between 2010 and 2015.

```{r import, warning=FALSE}
data <- read_csv(paste(data_in,"cs_bisnode_panel.csv", sep = "/"))

# drop variables with many NAs
data <- data %>%
  select(-c(COGS, finished_prod, net_dom_sales, net_exp_sales, wages)) %>%
  filter(year !=2016)

#panel to use
data <- data %>%
  filter(year >= 2010,
         year <= 2015)
```

## Label engineering
I add the missing year and company id combinations; I also identify the companies that are "alive", i.e. sales greater than 0 and no missing value for sales 

```{r}
# add all missing year and comp_id combinations -
# originally missing combinations will have NAs in all other columns
data <- data %>%
  complete(year, comp_id)

# generate status_alive; if sales larger than zero and not-NA, then firm is alive
data  <- data %>%
  mutate(status_alive = sales > 0 & !is.na(sales) %>%
           as.numeric(.))

```

## Constructing the Target
### Employment
Ideally, to identify fast-growing firms, I would use employment: firms (with at least 5 or 10 employees, i.e. not too small) would be identified as fast-growing if their employment annualized growing rate were greater than a certain threshold (e.g. 20%). However, the variable for employment, labor_avg, expresses the monthly average employment in one year. I could look at other possible measures of growth, for example sales, but I believe fast growth of employment can better define fast-growing firms: sales could grow for one or two years just due to contingencies and non-structural growth; while, when a firm hires more employees, the expansions entails a more structural/intrinsic growth. 
Moreover, the variables labor_avg is noisy (there are 121990 NA values out of 236250 total observations, and 316 0 values) but also sales is almost as noisy (72386 NA and 28864 zeros), and the lost in observations is almost the same. Therefore, I choose to proceed with employment.

First, I remove the missing values from labor_avg and I drop observations where labor_avg==0.
Then, I look at the distribution (log does not change)

```{r}

Hmisc::describe(data$labor_avg)
#table(data$labor_avg)
Hmisc::describe(data$sales)
#table(data$sales)

# drop missing
data <- data %>%
  filter(!is.na(labor_avg))

# drop those that are 0
data <- data %>%
  filter(labor_avg>0.0069)


labor_avg_graph <- ggplot(data, aes(x=labor_avg)) +
  geom_histogram(binwidth = 0.1, fill = color[1], color = color.outline, alpha = 0.8, size = 0.1) +
  ylab("count") +
  xlab("labor_avg") +
  scale_x_continuous(expand = c(0.00,0.00),limits=c(0,5), breaks = seq(0,5, 0.5)) +
  theme_bg()
labor_avg_graph

#ln
data <- data %>%
  mutate(ln_labor_avg = log(labor_avg+1))

Hmisc::describe(data$ln_labor_avg)

ln_labor_avg_graph <- ggplot(data, aes(x=ln_labor_avg)) +
  geom_histogram(binwidth = 0.1, fill = color[1], color = color.outline, alpha = 0.8, size = 0.1) +
  ylab("count") +
  xlab("ln_labor_avg") +
  scale_x_continuous(expand = c(0.00,0.00),limits=c(0,3), breaks = seq(0,3, 0.5)) +
  theme_bg()
ln_labor_avg_graph

```

#### Target variable
I construct the annual growth rate variable for the labor_avg. I look at quantiles and I consider as fast growing those firms with growth above the 80th percentile (fast_growth is the target variable and it is per year).

```{r}
#define target

# generate annual employment growth rate
data <- data %>% 
  group_by(comp_id) %>%
  mutate(growth_labor = c(NA,diff(labor_avg))/lag(labor_avg, 1))

Hmisc::describe(data$growth_labor)
growth_labor_80th <- quantile(data$growth_labor, 0.8, na.rm=TRUE)
growth_labor_80th 

#target
data <- data %>%
  group_by(comp_id) %>%
  mutate(fast_growth = ifelse(growth_labor > growth_labor_80th, 1, 0))
#above the 80th percentile
Hmisc::describe(data$fast_growth)

```

## Sales
First, I remove negative sales, create the logarithm of sales, re-scaled dividing by 1m, and growth rate. 
Then, I replace with 0 sales of new firms.

```{r}
summary(data$sales) # There will be NAs, we'll drop them soon

data <- data %>%
  mutate(sales = ifelse(sales < 0, 1, sales),
         ln_sales = ifelse(sales > 0, log(sales), 0),
         sales_mil=sales/1000000,
         sales_mil_log = ifelse(sales > 0, log(sales_mil), 0))
#growth rate of sales
data <- data %>%
  group_by(comp_id) %>%
  mutate(d1_sales_mil_log = sales_mil_log - Lag(sales_mil_log, 1) ) %>%
  ungroup()


# replace w 0 for new firms + add dummy to capture it
data <- data %>%
  mutate(age = (year - founded_year) %>%
           ifelse(. < 0, 0, .),
         new = as.numeric(age <= 1) %>% #  (age could be 0,1 )
           ifelse(balsheet_notfullyear == 1, 1, .),
         d1_sales_mil_log = ifelse(new == 1, 0, d1_sales_mil_log),
         new = ifelse(is.na(d1_sales_mil_log), 1, new),
         d1_sales_mil_log = ifelse(is.na(d1_sales_mil_log), 0, d1_sales_mil_log))
```

## Cross section
I retain observations for 2013 for firms that are alive, and that have sales between 1000 and 10m euros. Moreover, I remove those firms that have missing values for fast_growth (these are the new firms that do not have employment data for 2012).

```{r}
# look at cross section
#growth based on (2013-2012)/2012
data <- data %>%
  filter((year==2013) & (status_alive==1))%>%
  # look at firms below 10m euro revenues and above 1000 euros
  filter(!(sales_mil > 10)) %>%
  filter(!(sales_mil < 0.001))


Hmisc::describe(data$fast_growth)

data <- data %>%
  filter(!is.na(fast_growth))
```

## Feature engineering 
### Industry and Firms' characteristics
I change some industry category codes and define some additional firm characteristics: squared age, foreign management, gender of the CEO, firm HQ location.

```{r}
# change some industry category codes
data <- data %>%
  mutate(ind2_cat = ind2 %>%
           ifelse(. > 56, 60, .)  %>%
           ifelse(. < 26, 20, .) %>%
           ifelse(. < 55 & . > 35, 40, .) %>%
           ifelse(. == 31, 30, .) %>%
           ifelse(is.na(.), 99, .)
           )

table(data$ind2_cat)

# Firm characteristics
data <- data %>%
  mutate(age2 = age^2,
         foreign_management = as.numeric(foreign >= 0.5),
         gender_m = factor(gender, levels = c("female", "male", "mix")),
         m_region_loc = factor(region_m, levels = c("Central", "East", "West")))

```


### Financial variables
I look at financial variables: negative values of assets are changed to 0 (because they cannot be negative); I create total_asset variable which includes intangible, current, and fixed assets; I also create ratios for these financial variables. 
Moreover, I create flags (for errors) and winsorizing tails (for variables that are mostly between -1 and 1).

```{r, warning=FALSE}
# assets can't be negative. Change them to 0 and add a flag.
data <-data  %>%
  mutate(flag_asset_problem=ifelse(intang_assets<0 | curr_assets<0 | fixed_assets<0,1,0  ))
table(data$flag_asset_problem)

data <- data %>%
  mutate(intang_assets = ifelse(intang_assets < 0, 0, intang_assets),
         curr_assets = ifelse(curr_assets < 0, 0, curr_assets),
         fixed_assets = ifelse(fixed_assets < 0, 0, fixed_assets))

# generate total assets
data <- data %>%
  mutate(total_assets_bs = intang_assets + curr_assets + fixed_assets)
summary(data$total_assets_bs)


pl_names <- c("extra_exp","extra_inc",  "extra_profit_loss", "inc_bef_tax" ,"inventories",
              "material_exp", "profit_loss_year", "personnel_exp")
bs_names <- c("intang_assets", "curr_liab", "fixed_assets", "liq_assets", "curr_assets",
              "share_eq", "subscribed_cap", "tang_assets" )

# divide all pl_names elements by sales and create new column for it
data <- data %>%
  mutate_at(vars(pl_names), funs("pl"=./sales))

# divide all bs_names elements by total_assets_bs and create new column for it
data <- data %>%
  mutate_at(vars(bs_names), funs("bs"=ifelse(total_assets_bs == 0, 0, ./total_assets_bs)))


# Flags and winsorizing tails

# Variables that represent accounting items that cannot be negative (e.g. materials)
zero <-  c("extra_exp_pl", "extra_inc_pl", "inventories_pl", "material_exp_pl", "personnel_exp_pl",
           "curr_liab_bs", "fixed_assets_bs", "liq_assets_bs", "curr_assets_bs", "subscribed_cap_bs",
           "intang_assets_bs")

data <- data %>%
  mutate_at(vars(zero), funs("flag_high"= as.numeric(.> 1))) %>%
  mutate_at(vars(zero), funs(ifelse(.> 1, 1, .))) %>%
  mutate_at(vars(zero), funs("flag_error"= as.numeric(.< 0))) %>%
  mutate_at(vars(zero), funs(ifelse(.< 0, 0, .)))


# for vars that could be any, but are mostly between -1 and 1
any <-  c("extra_profit_loss_pl", "inc_bef_tax_pl", "profit_loss_year_pl", "share_eq_bs")

data <- data %>%
  mutate_at(vars(any), funs("flag_low"= as.numeric(.< -1))) %>%
  mutate_at(vars(any), funs(ifelse(.< -1, -1, .))) %>%
  mutate_at(vars(any), funs("flag_high"= as.numeric(.> 1))) %>%
  mutate_at(vars(any), funs(ifelse(.> 1, 1, .))) %>%
  mutate_at(vars(any), funs("flag_zero"= as.numeric(.== 0))) %>%
  mutate_at(vars(any), funs("quad"= .^2))


# dropping flags with no variation
variances<- data %>%
  select(contains("flag")) %>%
  apply(2, var, na.rm = TRUE) == 0

data <- data %>%
  select(-one_of(names(variances)[variances]))
```

### Additional characteristics
From CEOs ages, I can categorize them into young, old (or missing), and create a dummy for young CEOs. Furthermore, I create factors for urban and industry category.

```{r}
# CEO age
data <- data %>%
  mutate(ceo_age = year-birth_year,
         flag_low_ceo_age = as.numeric(ceo_age < 25 & !is.na(ceo_age)),
         flag_high_ceo_age = as.numeric(ceo_age > 75 & !is.na(ceo_age)),
         flag_miss_ceo_age = as.numeric(is.na(ceo_age)))

data <- data %>%
  mutate(ceo_age = ifelse(ceo_age < 25, 25, ceo_age) %>%
           ifelse(. > 75, 75, .) %>%
           ifelse(is.na(.), mean(., na.rm = TRUE), .),
         ceo_young = as.numeric(ceo_age < 40))

# create factors
data <- data %>%
  mutate(urban_m = factor(urban_m, levels = c(1,2,3)),
         ind2_cat = factor(ind2_cat, levels = sort(unique(data$ind2_cat))))
```

### Factor target
I create a factor for the target variable fast_growth: there are 11788 non-fast-growing firms and 2999 fast-growing

```{r}
data <- data %>%
  mutate(fast_growth_f = factor(fast_growth, levels = c(0,1)) %>%
           recode(., `0` = 'no_fast_growth', `1` = "fast_growth"))

table(data$fast_growth_f)
```

## Graphical analysis
### Sales

```{r}
# Sales
data <- data %>%
  mutate(sales_mil_log_sq=sales_mil_log^2)

graph_1 <- ggplot(data = data, aes(x=sales_mil_log, y=as.numeric(fast_growth))) +
  geom_point(size=2,  shape=20, stroke=2, fill="blue", color="blue") +
  geom_smooth(method = "lm", formula = y ~ poly(x,2), color=color[4], se = F, size=1)+
  geom_smooth(method="loess", se=F, colour=color[5], size=1.5, span=0.9) +
  labs(x = "sales_mil_log",y = "fast_growth") +
  theme_bg()
graph_1
save_fig("graph_1", output, "small")


ols_s <- lm(fast_growth~sales_mil_log+sales_mil_log_sq,
                data = data)
summary(ols_s)

# Sales change
# lowess
Hmisc::describe(data$d1_sales_mil_log) # no missing

graph_2<-ggplot(data = data, aes(x=d1_sales_mil_log, y=as.numeric(fast_growth))) +
  geom_point(size=0.1,  shape=20, stroke=2, fill=color[2], color=color[2]) +
  geom_smooth(method="loess", se=F, colour=color[1], size=1.5, span=0.9) +
 labs(x = "Growth rate (Diff of ln sales)",y = "fast_growth") +
 theme_bg() +
 scale_x_continuous(limits = c(-7,10), breaks = seq(-7,10, 5))
graph_2
save_fig("graph_2", output, "small")


# Winsorization
# generate variables
Hmisc::describe(data$d1_sales_mil_log)
#very few firms outside -1,1 range
data <- data %>%
  mutate(flag_low_d1_sales_mil_log = ifelse(d1_sales_mil_log < -1, 1, 0),
         flag_high_d1_sales_mil_log = ifelse(d1_sales_mil_log > 1, 1, 0),
         d1_sales_mil_log_mod = ifelse(d1_sales_mil_log < -1, -1,
                                       ifelse(d1_sales_mil_log > 1, 1, d1_sales_mil_log)),
         d1_sales_mil_log_mod_sq = d1_sales_mil_log_mod^2
         )

# no more imputation, drop obs if key vars missing
data <- data %>%
  filter(!is.na(liq_assets_bs),!is.na(foreign), !is.na(ind))

# drop missing
data <- data %>%
  filter(!is.na(age),!is.na(foreign), !is.na(material_exp_pl), !is.na(m_region_loc))
Hmisc::describe(data$age)

# drop unused factor levels
data <- data %>%
  mutate_at(vars(colnames(data)[sapply(data, is.factor)]), funs(fct_drop))

Hmisc::describe(data$d1_sales_mil_log_mod)

graph_3<-ggplot(data = data, aes(x=d1_sales_mil_log_mod, y=as.numeric(fast_growth))) +
  geom_point(size=0.1,  shape=20, stroke=2, fill=color[2], color=color[2]) +
  geom_smooth(method="loess", se=F, colour=color[1], size=1.5, span=0.9) +
  labs(x = "Growth rate (Diff of ln sales)",y = "fast_growth") +
  theme_bg() +
  scale_x_continuous(limits = c(-1,1), breaks = seq(-1,1, 0.5))
graph_3
save_fig("graph_3", output, "small")

graph_4<-ggplot(data = data, aes(x=d1_sales_mil_log, y=d1_sales_mil_log_mod)) +
  geom_point(size=0.1,  shape=20, stroke=2, fill=color[2], color=color[2]) +
  labs(x = "Growth rate (Diff of ln sales) (original)",y = "Growth rate (Diff of ln sales) (winsorized)") +
  theme_bg() +
  scale_x_continuous(limits = c(-7,10), breaks = seq(-7,10, 1)) +
scale_y_continuous(limits = c(-3,3), breaks = seq(-3,3, 1))
graph_4
save_fig("graph_4", output, "small")

```